Linear Stochastic Approximation- Constant Step-Size and Iterate Averaging

### 2017-05-18 illustrate.tex
discussion
up to sec 5

\subsection{Illustrative Examples}
In this section, we present some illustrative examples and make some useful remarks about the same.
\begin{example}\label{ex:pdas}
Matrices $A_1=\begin{bmatrix} 2 &1 \\-1 &0\end{bmatrix}$$A_2=\begin{bmatrix}1 & -1\\ 1 &0 \end{bmatrix}$ and $A_3=\begin{bmatrix} 1 & 10-\epsilon \\ 0 &1 \end{bmatrix},0<\epsilon<0.1$ are not positive definite. However choosing $U_1=\begin{bmatrix} \frac{1}{\sqrt{2}}& -\frac{1}{\sqrt{2}}\\ -\frac{1}{\sqrt{2}} &\frac{1}{\sqrt{2}} \end{bmatrix}$, $U_2=\begin{bmatrix} \frac{\sqrt{2}}{1-i\sqrt{3}} & \frac{\sqrt{2}}{1+i\sqrt{3}} \\ -\frac{1}{\sqrt{2}} &\frac{1}{\sqrt{2}}\end{bmatrix}$ and $U_3=\begin{bmatrix} 1 & 0\\ 0 &\frac{1}{10} \end{bmatrix}$, we can see that matrices $J_i=U_i^{-1}A_i U_i,i=1,2,3$ are positive definite.
\end{example}
The above example \Cref{ex:pdas} illustrates the use of appropriate $U_i,i=1,2,3$ matrices to transform Hurwitz problems into positive definite problems. In particular, problem $P^2$ involves the use of a complex matrix $U_2$.
\begin{example}\label{ex:geo}
Consider the one dimensional case where $A_t=\rho$ for some $0<\rho<1$, $b_t$ a bounded $i.i.d$ zero mean random variable with variance $\sigma^2$, and $\ts=0$. We know that $e_t=(1-\alpha\rho)^t e_0+\sum_{s=1}^t (1-\alpha \rho)^{t-s}\alpha b_s$ and the MSE is given by
\begin{align*}
\EE{\norm{\thh_t}^2}&=\frac{1}{(t+1)^2}\left( (\alpha\rho)^{-1}(1-\alpha\rho)^{t+1}) \theta_0+ \sum_{s=1}^t (\alpha\rho)^{-1}(1-\alpha \rho)^{t-s+1} \alpha b_s\right)^2\\
&\leq (\alpha\rho)^{-2}\left(\frac{\norm{\theta_0}^2}{t^2}+\frac{\alpha^2\sigma^2}{t}\right)
\end{align*}
\end{example}
The above example helps to interpret the error dynamics of \Cref{eq:lsa} in terms of sum of a geometric series with common factor $\alpha\rho$.
\begin{comment}
\begin{example}
Consider deterministic problems $P^1$, $P^2$ and $P^3$ with $A_{P^1}=\begin{bmatrix} 10 &100\\ 0 &10\end{bmatrix}$, $A_{P^2}=\begin{bmatrix} 10 &9.99\\ 0 &10\end{bmatrix}$, $A_{P^3}=\begin{bmatrix} 10 &0 \\ 0 &10\end{bmatrix}$, $\sigma^2_{A_{P^i}}=\sigma_{b_{P^i}}=0,\,i=1,2,3$. Note that $P^1$, $P^2$ and $P^3$ are respectively H, PD, SPD respectively.
\end{example}
\input{plts}
\end{comment}

>>>>

%!TEX root =  flsa.tex
%\subsection{Illustrative Examples}
%In this section, we present some illustrative examples and make some useful remarks about the same.
\if0
\begin{example}\label{ex:pdas}
Matrices $A_1=\begin{bmatrix} 2 &1 \\-1 &0\end{bmatrix}$,
$A_2=\begin{bmatrix}1 & -1\\ 1 &0 \end{bmatrix}$ and $A_3=\begin{bmatrix} 1 & 10-\epsilon \\ 0 &1 \end{bmatrix},0<\epsilon<0.1$ are not positive definite. However choosing $U_1=\begin{bmatrix} \frac{1}{\sqrt{2}}& -\frac{1}{\sqrt{2}}\\ -\frac{1}{\sqrt{2}} &\frac{1}{\sqrt{2}} \end{bmatrix}$, $U_2=\begin{bmatrix} \frac{\sqrt{2}}{1-i\sqrt{3}} & \frac{\sqrt{2}}{1+i\sqrt{3}} \\ -\frac{1}{\sqrt{2}} &\frac{1}{\sqrt{2}}\end{bmatrix}$ and $U_3=\begin{bmatrix} 1 & 0\\ 0 &\frac{1}{10} \end{bmatrix}$, we can see that matrices $J_i=U_i^{-1}A_i U_i,i=1,2,3$ are positive definite.
\end{example}
The above example \Cref{ex:pdas} illustrates the use of appropriate $U_i,i=1,2,3$ matrices to transform Hurwitz problems into positive definite problems. In particular, the second problem involves the use of a complex matrix $U_2$.
\fi
\todoc{I commented out the Hurwitz example. I did not find it very useful.}
The following example can shed further light on the structure of the bound:%
\todoc{I am wondering whether this could replace Theorem 2?}
\begin{example}\label{ex:geo}
Consider the one dimensional case where $A_t=\rho$ for some $0<\rho<1$, $b_t$ a bounded \iid zero mean random variable with variance $\sigma^2$, and $\ts=0$. We can easily calculate 
that $e_t=(1-\alpha\rho)^t e_0+\sum_{s=1}^t (1-\alpha \rho)^{t-s}\alpha b_s$ and thus the MSE becomes \todoc{Check what happens with $t=0$!}
\begin{align*}
\EE{\normsm{\thh_t}^2}&=\frac{1}{(t+1)^2}\left( (\alpha\rho)^{-1}(1-\alpha\rho)^{t+1}) \theta_0+ \sum_{s=1}^t (\alpha\rho)^{-1}(1-\alpha \rho)^{t-s+1} \alpha b_s\right)^2\\
&\leq (\alpha\rho)^{-2}\left(\frac{\norm{\theta_0}^2}{t^2}+\frac{\alpha^2\sigma^2}{t}\right)\,.
\end{align*}
\end{example}
%The above example helps to interpret the error dynamics of \Cref{eq:lsa} in terms of sum of a geometric series with common factor $\alpha\rho$.
\begin{comment}
\begin{example}
Consider deterministic problems $P^1$, $P^2$ and $P^3$ with $A_{P^1}=\begin{bmatrix} 10 &100\\ 0 &10\end{bmatrix}$, $A_{P^2}=\begin{bmatrix} 10 &9.99\\ 0 &10\end{bmatrix}$, $A_{P^3}=\begin{bmatrix} 10 &0 \\ 0 &10\end{bmatrix}$, $\sigma^2_{A_{P^i}}=\sigma_{b_{P^i}}=0,\,i=1,2,3$. Note that $P^1$, $P^2$ and $P^3$ are respectively H, PD, SPD respectively.
\end{example}
\input{plts}
\end{comment}
